### 2020-11-25 paper/main.tex
paper outline

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{Machines are Among Us}

\author{Zach Minot\\
Georgia Institute of Technology\\
2nd Year Undergraduate, CS\\
{\tt\small zjminot@gatech.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Charles Gunn\\
Georgia Institute of Technology\\
2nd Year Undergraduate, CS \& Math\\
{\tt\small cgunn30@gatech.edu}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\subsection{Adverserial Networks}
\subsection{Multi-agent Communication}

\section{Approach}
\subsection{Deductive Situation}
\subsection{Modeling Interpretation and Communication}
\subsection{Zero-sum Target}
\subsection{Training Scheme}
\subsection{Challenges}

\section{Results}
% talk about our goal for a qualitatively "good" communication
% session.
\subsection{Oscillating Scores}
% talk about problems we saw frequently. show examples of "good" runs
% and bad runs
\subsection{Situation Hyperparameters}
% grid search results.
\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
\subsection{Future Directions}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2020-11-25 train.py

@@ -194,7 +194,7 @@ def main():
         "P": 10,
         "I": 2,
         "EPOCHS": 6,
-        "EPOCH_LENGTH": 512,
+        "EPOCH_LENGTH": 1024,
         "VIEW_CHANCE": 0.4,
         "SABOTAGE_CHANCE": 0.0,
         "TRAIN_CREW_FIRST": False,

### 2020-11-28 paper/main.tex
first pass at the introduction

@@
 
-%%%%%%%%% ABSTRACT
+%%%%%%%%% ABSTRACTcommunicate
 \begin{abstract}
@@
 \section{Introduction}
+
+To what extent can neural network models communicate with each other and discover
+each other's identity? How would they use this information in a competitive setting?
+For example, in a social deduction game, players attempt to uncover each other's
+hidden allegiance---typically with one "good" team and one "bad" team.
+Players must utilize deductive reasoning to find the truth or instead
+lie to keep their role hidden. In this paper, we explore 
+if neural networks can be successfully trained to
+compete in a scenario such as this, and how would the opposing parties interact
+during the period of debate.
+
+\subsection{Among Us}
+Among Us is a currently popular social deduction game,
+where the "imposters" attempt to sabotage and kill all of the "crewmates". Crewmmates have
+to complete tasks and figure out who the imposters are and eliminate them before the imposters
+win.
+At certain points in the game, after periods of no direct communication, players 
+debate the roles of each individual based on information previously acquired through
+their personal experience. At the end of this discussion, every player votes on a single
+player to be eliminated. The player with the most votes is eliminated, and if there
+is a tie, no one is voted out. We chose to emulate this game based on
+the overall simplicity of the two roles and the requirement of communication
+for either party to succeed. If the crew do not exchange information 
+and all vote the same person, 
+the vote could result in a tie or a crew being eliminated.
+If the imposters do not bluff, the crew can easily spot the liars among the group. 
+This provides ample room to explore and experiment with the communication between
+the two opposing parties.
 \subsection{Adverserial Networks}
+Within this design space, there are adversarial parties working against each other.
+In the deep learning realm, adversarial situations appear in adversarial examples
+[https://arxiv.org/pdf/1412.6572.pdf] and within GANs (generative adversarial networks)
+[https://proceedings.neurips.cc/paper/2014/hash/5ca3e9b122f61f8f06494c97b1afccf3-Abstract.html].
+In particular, the latter often designs a contest between two neural networks, in the form
+of a zero-sum game.
+We build upon these concepts and foundations in our work.
 \subsection{Multi-agent Communication}
-
+Inherently, a social deduction game requires multiple agents to be trained and contested.
+This has been explored within the deep learning problem space with multi-agent subproblems.
+Both cooperative [https://arxiv.org/pdf/1602.02672.pdf] [https://arxiv.org/pdf/1605.06676.pdf] 
+and adversarial [https://arxiv.org/pdf/1610.06918.pdf] communication has been experimented with,
+showing that models can effective share and also selectively protect information.
+We reference these approaches we generate active adversarial communication between 
+neural network models.
 \section{Approach}

### 2020-11-29 paper/main.tex
real references

@@
 Within this design space, there are adversarial parties working against each other.
-In the deep learning realm, adversarial situations appear in adversarial examples
-[https://arxiv.org/pdf/1412.6572.pdf] and within GANs (generative adversarial networks)
-[https://proceedings.neurips.cc/paper/2014/hash/5ca3e9b122f61f8f06494c97b1afccf3-Abstract.html].
+In the deep learning realm, adversarial situations appear in adversarial examples~\cite{AdverserialEx} and within GANs (generative adversarial networks)
+~\cite{NIPS2014_5ca3e9b1}
 In particular, the latter often designs a contest between two neural networks, in the form
@@
 This has been explored within the deep learning problem space with multi-agent subproblems.
-Both cooperative [https://arxiv.org/pdf/1602.02672.pdf] [https://arxiv.org/pdf/1605.06676.pdf] 
-and adversarial [https://arxiv.org/pdf/1610.06918.pdf] communication has been experimented with,
+Both cooperative~\cite{DBLP:journals/corr/FoersterAFW16}~\cite{DBLP:journals/corr/FoersterAFW16a} 
+and adversarial ~\cite{DBLP:journals/corr/AbadiA16} communication has been experimented with,
 showing that models can effective share and also selectively protect information.

### 2020-11-29 train.py

@@ -172,8 +172,8 @@ def grid_search(param_dict):
         "saves", datetime.datetime.now().strftime("%Y-%m-%d_%H-%M-%S") + "_GRID"
     )
 
-    VIEW_GRID = [0.2, 0.4, 0.6, 0.8, 1]
-    SAB_GRID = [0, 0.25, 0.5, 0.75, 1]
+    VIEW_GRID = [0.4, 0.6, 0.8]
+    SAB_GRID = [0, 0.25, 0.5, 0.75]
     for v_chance in VIEW_GRID:
         for s_chance in SAB_GRID:
             param_dict["VIEW_CHANCE"] = v_chance
@@ -206,9 +206,9 @@ def main():
         "SAVE_EPOCH_FREQ": 2,
     }
     # run the grid search
-    # grid_search(param_dict)
+    grid_search(param_dict)
     # just train once. dont save.
-    train(TrainParams(**param_dict), verbose=True)
+    # train(TrainParams(**param_dict), verbose=True)
 
 
 if __name__ == "__main__":

### 2020-11-30 paper/main.tex
added the model diagram

@@
 \section{Introduction}
-
 To what extent can neural network models communicate with each other and discover
@@
 during the period of debate.
-
 \subsection{Among Us}
@@
 \subsection{Modeling Interpretation and Communication}
+\begin{figure*}
+   \begin{center}
+      \includegraphics[width=0.8 \textwidth]{img/model.png}
+   \end{center}
+      \caption{Diagram of the Agent model. The red section is the perception LSTM,
+      which takes in a sequence of events. The blue section is the communication
+      LSTM, which recieves messages, and generates messages using the green MLP.
+      Finally, the purple section is the voting MLP, which produces the agent's
+      vote vector.}
+   \label{fig:model}
+   \end{figure*}
+
 \subsection{Zero-sum Target}

### 2020-11-30 plot.py
heatmap plots for grid searches

@@ -1,0 +1,52 @@
+import pandas as pd
+import seaborn as sns
+import os
+import json
+from parse import parse
+
+
+def grid_search_df(grid_dir):
+    rows = []
+    for sub in os.scandir(os.path.join("saves", grid_dir)):
+        output = [
+            line.strip()
+            for line in open(os.path.join(sub.path, "output.txt")).readlines()
+        ]
+        params = json.load(open(os.path.join(sub.path, "params.json")))
+        params["FINAL_SCORE"] = parse("Batch {b}; Crew Score: {s:f}", output[-1])["s"]
+        rows.append(params)
+    return pd.DataFrame(rows)
+
+
+def plot_grid_search(grid_dir, axes, query=None):
+    ax1, ax2 = axes
+    df = grid_search_df(grid_dir)
+    if query:
+        q_str = " & ".join(f"{k} == {v}" for k, v in query.items())
+        df = df.query(q_str)
+    plot = sns.heatmap(df.pivot(ax1, ax2, "FINAL_SCORE"))
+
+    plot_dir = os.path.join("plots", grid_dir)
+    if not os.path.exists(plot_dir):
+        os.makedirs(plot_dir)
+    name = f"{ax1[:4]}-{ax2[:4]}"
+    if query:
+        name += "_" + "-".join(f"{k}{v}" for k, v in query.items())
+    fig = plot.get_figure()
+    fig.savefig(os.path.join(plot_dir, f"{name}.png".lower()))
+
+
+def main():
+    # plot_grid_search("2020-11-24_00-18-06_GRID", ("VIEW_CHANCE", "SABOTAGE_CHANCE"))
+    plot_grid_search(
+        "2020-11-26_22-56-46_GRID",  # grid search folder
+        ("M", "ROUNDS"),  # two axes to create the plot over
+        query={
+            "N": 16,
+            "SABOTAGE_CHANCE": 0.5,
+        },  # filters (to make the data-points unique)
+    )
+
+
+if __name__ == "__main__":
+    main()

### 2020-12-01 plot.py
plotting runs

@@ -4,26 +4,61 @@ import os
 import json
 from parse import parse
 
+sns.set_style("whitegrid")
 
-def grid_search_df(grid_dir):
+
+def get_output_params(run_dir):
+    raw_log = [
+        line.strip() for line in open(os.path.join(run_dir, "output.txt")).readlines()
+    ]
+    output = []
+    for line in raw_log:
+        if "Epoch" in line:
+            output.append([])
+            continue
+        r = parse("Batch {batch:d}; Crew Score: {score:f}", line)
+        if not r:
+            continue
+        output[-1].append(r)
+    params = json.load(open(os.path.join(run_dir, "params.json")))
+    return output, params
+
+
+def plot_run(run_dir):
+    output, params = get_output_params(os.path.join("saves", run_dir))
     rows = []
-    for sub in os.scandir(os.path.join("saves", grid_dir)):
-        output = [
-            line.strip()
-            for line in open(os.path.join(sub.path, "output.txt")).readlines()
-        ]
-        params = json.load(open(os.path.join(sub.path, "params.json")))
-        params["FINAL_SCORE"] = parse("Batch {b}; Crew Score: {s:f}", output[-1])["s"]
-        rows.append(params)
-    return pd.DataFrame(rows)
+    for e, epoch in enumerate(output):
+        rows.extend(
+            {"Score": r["score"], "Batch": params["EPOCH_LENGTH"] * e + r["batch"]}
+            for r in epoch
+        )
+    df = pd.DataFrame(rows)
+
+    plot = sns.lineplot(data=df, x="Batch", y="Score")
+    xticks = [0] + [params["EPOCH_LENGTH"] * (e + 1) for e in range(len(output))]
+    plot.set_xticks(xticks)
+    plot.set_xticklabels(range(len(output) + 1))
+    plot.set_xlabel("Epoch")
+
+    fig = plot.get_figure()
+    file_name = os.path.join("plots", run_dir + ".png")
+    if not os.path.exists(os.path.dirname(file_name)):
+        os.makedirs(os.path.dirname(file_name))
+    fig.savefig(file_name)
 
 
 def plot_grid_search(grid_dir, axes, query=None):
     ax1, ax2 = axes
-    df = grid_search_df(grid_dir)
+    rows = []
+    for sub in os.scandir(os.path.join("saves", grid_dir)):
[…]

### 2020-12-01 paper/main.tex
1/4 of first pass of approach, oops

--- 2020-11-29 paper/main.tex
@@
 \section{Approach}
+We deconstructed a standard voting round of Among Us into three stages: 
+communicationless information gain,
+argument and debate, and the final vote. Building off of this, we decided 
+to break our standard player model into a perception stage, 
+communication stage, and voting stage. Each satge feeds into the next until the final
+vote occurs to eliminate one of the models within the communicating group.
 \subsection{Deductive Situation}
+During the period of communication in Among Us, the crew must do tasks
+and gain information while the imposters must sabotage and kill the crew. We decided
+to simplify the game by both removing the tasks and killing and making the entire
+perception of each player predetermined.
 \subsection{Modeling Interpretation and Communication}
+\begin{figure*}
+   \begin{center}
+      \includegraphics[width=0.8 \textwidth]{img/model.png}
+   \end{center}
+      \caption{Diagram of the Agent model. The red section is the perception LSTM,
+      which takes in a sequence of events. The blue section is the communication
+      LSTM, which recieves messages, and generates messages using the green MLP.
+      Finally, the purple section is the voting MLP, which produces the agent's
+      vote vector.}
+   \label{fig:model}
+\end{figure*}
+
 \subsection{Zero-sum Target}
+The last stage is the most simple one, voting. The model simple takes the concetnated
+hidden outputs from the communication stage and feeds them through
+multi-layer perceptron layers. This finalizes as a player length probability vector
+of a confidence that a specific player (at that index) should be voted out.
+
+The "crew score" is the sum of all votes of any player for an imposter. The imposter loss
+is the crew score, and the crew loss is the negation.
+Relate back to GANs, zero-sum game so that adversarial works.
 \subsection{Training Scheme}
+There were multiple decisions we had to make when attempting to train the models.
+Imposter/Crew two different models, multitude of different hyperparameters and
+sizes of inputs/outputs.
 \subsection{Challenges}
+The main challenge in building and running the model
+came mainly in the form of training time, gradient overlap, 
+and hyperparameter search.
+
+Another important challenge to recognize is the extreme "black box" architecture
+of the model. With our current model iteration, we have no current approach to visualizing
+exactly what the model is doing, especially with communication. Therefore there are
+assumptions and estimations when creating conclusions about the model.
 

### 2020-12-02 paper/main.tex
editing the approach section

--- 2020-11-30 paper/main.tex
@@
 \section{Approach}
+In order to examine the interactions between multiple agents -- some of who are
+secretly imposters who must ``lie'', we chose to construct an ``Among Us''-esque scenario
+for our models to partake in. On a high level, we wanted each agent to 
+first collect information
+independant of the others. Then, there should be some phase of communication between the
+models -- qualitatively, it is during this stage that the agents will attempt to
+deduce who the imposters are, an the imposters will attempt to blend in. Finally, the
+agents all vote on who they think is a likely imposter. The upcoming sections
+explain how we chose to model each of these phases in greater detail.
 \subsection{Deductive Situation}
+During the period of communication in Among Us, the crew must do tasks
+and gain information while the imposters must sabotage and kill the crew. We decided
+to simplify the ``game'' by both removing the tasks and killing and making the entire
+perception of each player predetermined.
+
+Specifically, each agent is given as input a matrix consisting
+of $N$ events. During each event, the agent ``sees'' some subset of the other players
+(sight is reflexive and symmetric, but not transitive).
+They also may experience a ``sabotage'', which means they are in the prescence
+of an imposter who is sabotaging. They cannot see the imposter, but the imposter
+can see them during this event. Ultimately, each agent will recieve
+a $N \times (P + 1)$ matrix, where $P$ is the total number of players -- the first
+$P$ values of a row indicate who the agent is seeing, and the final value indicates
+a sabotage.
+
+These event matrices are generated randomly using four key parameters: the total number
+of players ($P$), the number of those players who are imposters ($I$), the chance that
+any given pair of players will see one another during an event (view chance), and the 
+chance that any given imposter will sabotage during an  event (sabotage chance).
 \subsection{Modeling Interpretation and Communication}
@@
 \end{figure*}
+In order to process the input events, our agent model has an LSTM, which
+generates $c_N$ and $h_N$, which are used as the initial inputs
+$h_0$ and $c_0$ to the next phase:
+communication. Communcation is also modeled with an LSTM. During each ``round''
+of communication, every agent contributes a message vector of size $M$ via
+a small MLP using $h_t$ as input. These messages are collected into a matrix
+of size $M \times P$, which is fed as input into each agent's LSTM so that
+their memory can be updated before the next round of communication -- there
+are $R$ rounds in total. We chose
+to model communication this way because it is a simple and symmetric way for the agents
+to pass information between each other in multiple rounds.
 
 \subsection{Zero-sum Target}
+The last stage is the most simple one -- voting. The model simple takes the $h_R$ and
+$c_R$ from the end of the communication LSTM and feeds them through
+a small MLP finalized with a softmax layer. This results in a probability vector
+of a confidence that a specific player should be ``voted out''.
+
+At the end of voting, we calculate a ``crew score''. This score is simply the
+maximum vote-off score that any imposter recieved, where votes
+are averaged across all agents. Clearly, the imposters would like to minimize the
+votes on themselves, so their loss function for training purposes is
+simply the crew score. Inversely, the crew's loss function is the negation of
+the crew score.
+\textbf{Zach: Relate back to GANs, zero-sum game so that adversarial works}
 \subsection{Training Scheme}
+There were multiple decisions we had to make when attempting to train the models.
+Imposter/Crew two different models, multitude of different hyperparameters and
+sizes of inputs/outputs.
 \subsection{Challenges}
+The main challenge in building and running the model
+came mainly in the form of training time, gradient overlap, 
+and hyperparameter search.
+
+Another important challenge to recognize is the extreme "black box" architecture
+of the model. With our current model iteration, we have no current approach to visualizing
+exactly what the model is doing, especially with communication. Therefore there are
+assumptions and estimations when creating conclusions about the model.
 

### 2020-12-02 paper/main.tex
added some work to future directions

--- 2020-12-01 paper/main.tex
@@
 \subsection{Future Directions}
+This approach is just a start into understanding how neural networks
+communicate with one another. Although assumptions can be made,
+understanding the actual information being transferred between each model is
+a dark area. Innovative techniques must be found to analyze this information flow 
+in order to fully comprehend the strategy within the game.
 
+Furthermore, the results could help to explore more cryptographic use cases for neural networks.
+It was observed that the crew could identify the imposters with no prior information which leads us to
+believe the crew model had some sort of hidden code or tag to identify themselves.
+
+Finally, similar work in adversarial networks could potentially give rise to
+more techniques utilizing them. GANs are at the forefront of adversarial techniques, but possibly
+large multi-agent adervasarial communication networks could give heed to more good results.
 {\small

### 2020-12-02 paper/main.tex
Added some information to README and updated paper

@@
 simply the crew score. Inversely, the crew's loss function is the negation of
-the crew score.
-\textbf{Zach: Relate back to GANs, zero-sum game so that adversarial works}
+the crew score. This takes the form of a zero-sum game with similar application
+as in generative adversarial networks.
 \subsection{Training Scheme}
@@
 came mainly in the form of training time, gradient overlap, 
-and hyperparameter search.
+and hyperparameter search. As discussed previously, to help speed up training time
+and reduce gradient overlap between multiple different models training over the
+same dataset, we had to only train either one imposter or crew, and keep the rest constant.
+This limits the quick adaptivity, and may lead to the models attempting to train
+against the constant tcooperative models ratrher than against the adversarial model.
+
+Furthermore, the immense number of combinations of hyperparameters
+and input and outputs sizes, along with no precedent for recommended values,
+lead us to generalize our model significantly. Although this may seem like an ability for
+customizability, it severely reduces reproducability over small changes.
 
@@
 Finally, similar work in adversarial networks could potentially give rise to
-more techniques utilizing them. GANs are at the forefront of adversarial techniques, but possibly
+more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
 large multi-agent adervasarial communication networks could give heed to more good results.

### 2020-12-02 paper/main.tex
page number starts at 1 lol
added heatmap and some hyperparameter text

--- 2020-12-02 paper/main.tex
@@
 %\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\setcounter{page}{1}
 \begin{document}
@@
 neural network models.
-\section{Approach}
-We deconstructed a standard voting round of Among Us into three stages: 
-communicationless information gain,
-argument and debate, and the final vote. Building off of this, we decided 
-to break our standard player model into a perception stage, 
-communication stage, and voting stage. Each satge feeds into the next until the final
-vote occurs to eliminate one of the models within the communicating group.
-\subsection{Deductive Situation}
-During the period of communication in Among Us, the crew must do tasks
-and gain information while the imposters must sabotage and kill the crew. We decided
-to simplify the game by both removing the tasks and killing and making the entire
-perception of each player predetermined.
-\subsection{Modeling Interpretation and Communication}
 \begin{figure*}
@@
 \end{figure*}
+\section{Approach}
+In order to examine the interactions between multiple agents -- some of who are
+secretly imposters who must ``lie'', we chose to construct an ``Among Us''-esque scenario
+for our models to partake in. On a high level, we wanted each agent to 
+first collect information
+independant of the others. Then, there should be some phase of communication between the
+models -- qualitatively, it is during this stage that the agents will attempt to
+deduce who the imposters are, an the imposters will attempt to blend in. Finally, the
+agents all vote on who they think is a likely imposter. The upcoming sections
+explain how we chose to model each of these phases in greater detail.
+\subsection{Deductive Situation}
+During the period of communication in Among Us, the crew must do tasks
+and gain information while the imposters must sabotage and kill the crew. We decided
+to simplify the ``game'' by both removing the tasks and killing and making the entire
+perception of each player predetermined.
+
+Specifically, each agent is given as input a matrix consisting
+of $N$ events. During each event, the agent ``sees'' some subset of the other players
+(sight is reflexive and symmetric, but not transitive).
+They also may experience a ``sabotage'', which means they are in the prescence
+of an imposter who is sabotaging. They cannot see the imposter, but the imposter
+can see them during this event. Ultimately, each agent will recieve
+a $N \times (P + 1)$ matrix, where $P$ is the total number of players -- the first
+$P$ values of a row indicate who the agent is seeing, and the final value indicates
+a sabotage.
+
+These event matrices are generated randomly using four key parameters: the total number
+of players ($P$), the number of those players who are imposters ($I$), the chance that
+any given pair of players will see one another during an event (view chance), and the 
+chance that any given imposter will sabotage during an  event (sabotage chance).
+
+\subsection{Modeling Interpretation and Communication}
+In order to process the input events, our agent model has an LSTM, which
+generates $c_N$ and $h_N$, which are used as the initial inputs
+$h_0$ and $c_0$ to the next phase:
+communication. Communcation is also modeled with an LSTM. During each ``round''
+of communication, every agent contributes a message vector of size $M$ via
+a small MLP using $h_t$ as input. These messages are collected into a matrix
+of size $M \times P$, which is fed as input into each agent's LSTM so that
+their memory can be updated before the next round of communication -- there
+are $R$ rounds in total. We chose
+to model communication this way because it is a simple and symmetric way for the agents
+to pass information between each other in multiple rounds.
 
 \subsection{Zero-sum Target}
-The last stage is the most simple one, voting. The model simple takes the concetnated
-hidden outputs from the communication stage and feeds them through
-multi-layer perceptron layers. This finalizes as a player length probability vector
-of a confidence that a specific player (at that index) should be voted out.
+The last stage is the most simple one -- voting. The model simple takes the $h_R$ and
+$c_R$ from the end of the communication LSTM and feeds them through
+a small MLP finalized with a softmax layer. This results in a probability vector
+of a confidence that a specific player should be ``voted out''.
 
-The "crew score" is the sum of all votes of any player for an imposter. The imposter loss
-is the crew score, and the crew loss is the negation.
-Relate back to GANs, zero-sum game so that adversarial works.
+At the end of voting, we calculate a ``crew score''. This score is simply the
+maximum vote-off score that any imposter recieved, where votes
+are averaged across all agents. Clearly, the imposters would like to minimize the
+votes on themselves, so their loss function for training purposes is
+simply the crew score. Inversely, the crew's loss function is the negation of
+the crew score. This takes the form of a zero-sum game with similar application
+as in generative adversarial networks.
 \subsection{Training Scheme}
@@
 assumptions and estimations when creating conclusions about the model.
-
+\subsection{Situation Hyperparameters}
+To list the variable hyperparameters and input and outputs sizes for the player model,
+overall, we have batch size, number of epochs, epoch length, the global LSTM hidden layer size, 
+and the amount of players and imposters. For the perception phase, there is the
+chance a player will view another player, the chance a sabotage occurs, and the number of $N$ events.  
+The communication stage has variables the message size $M$ and the number of communication rounds
+$R$.
+\begin{figure*}
+   \begin{center}
+      \includegraphics[width=0.8 \textwidth]{img/grid_search.png}
+   \end{center}
+      \caption{A grid search heat map over the size parameters M (message vector) 
+      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs.
+      }
+   \label{fig:model}
+\end{figure*}
 \section{Results}
@@
 % and bad runs
-\subsection{Situation Hyperparameters}
+
 % grid search results.

### 2020-12-02 plot.py

@@ -83,7 +83,7 @@ def main():
     #     },  # filters (to make the data-points unique)
     # )
 
-    plot_run(os.path.join("2020-11-26_22-56-46_GRID", "n8_s0.0_m64_r6"))
+    plot_run(os.path.join("2020-11-30_21-02-40_GRID", "m20_r2"))
 
 
 if __name__ == "__main__":

### 2020-12-02 paper/main.tex
added part to results and started appendix
more additions, just pushing so i can take a break

@@
 There were multiple decisions we had to make when attempting to train the models.
+The two opposing models were trained
 Imposter/Crew two different models, multitude of different hyperparameters and
@@
 % session.
+Due to the unprecedented architecture, we decided our overall goals
+were to find the balance between imposter and crew
+score, locate trends within the variable changes, and attempt to 
+understand how the models communicate, to a degree. We conducted many
+training sessions over multiple different combinations of variables.
+
+A typical training session started with the first two initial epochs,
+as discussed previously
+
+Through our search, we found a trend to three different types of results:
+an imposter 'win', a crew 'win', and a convergence.
+An imposter win happens under certain circumstances where the crew are unable
+to employ a better strategy than the crew's equally voting all other candidates.
+A crew win occurs with the opposite---the crew can determine exactly who the imposters
+are, and crew vote for one imposter. A convergence happens to place itself in the middle,
+for what we assume to be a fair, balanced game between the two opposing parties.
+
+Due to resource constraints, we were not able to get as much 
+data as we had hoped for.
+This lead to a consistency issue, where the same variable combination would yield
+different results because of certain randomness within training the models.
 \subsection{Oscillating Scores}
-% talk about problems we saw frequently. show examples of "good" runs
-% and bad runs
+The hopeful goal was to find the set of variables that lead to not only a convergence,
+but an almost "tug-of-war" battle when one model trains against the other and vice versa.
+This is graphically shown via an oscillating crew score around the 
+eventual convergence crew score. This would mean that the two models
+are successfunlly balanced and able to improve their strategy with training time against
+the opposition.
+
+In an attempt to find a training session mathcing this quality
 
@@
 \subsection{Interpreting Communcation Vectors}
+Unfortunately, we could not 
 \subsection{Future Directions}
@@
 }
-
+\appendix
+\section{Reproducibility}
+\section{Framework}
 \end{document}

### 2020-12-02 paper/main.tex
added some information in results and approach

@@
 There were multiple decisions we had to make when attempting to train the models.
-The two opposing models were trained
-Imposter/Crew two different models, multitude of different hyperparameters and
-sizes of inputs/outputs.
+Similar to GANs, we decided the best approach to train the two adversarial models was to
+use alternating training to help find eventual convergence and juggle two different
+optimizations.
+
 \subsection{Challenges}
@@
 This limits the quick adaptivity, and may lead to the models attempting to train
-against the constant tcooperative models ratrher than against the adversarial model.
+against the constant cooperative models ratrher than against the adversarial model.
 
@@
 and input and outputs sizes, along with no precedent for recommended values,
-lead us to generalize our model significantly. Although this may seem like an ability for
-customizability, it severely reduces reproducability over small changes.
+lead us to generalize our model significantly. Although this offers the extended ability for
+customizability and exploration, it severely reduces reproducability over small changes.
 
@@
 
-A typical training session started with the first two initial epochs,
-as discussed previously
+A typical training session started with the first two alternating epochs,
+which were considered as the "initialization" of the two models. Training the imposters
+first gave them time to learn to note vote for each other. Then, the crew
+had learned the same thing on the next epoch. After this initial training,
+then the models started to significantly train against each other.
 
@@
 different results because of certain randomness within training the models.
+
 \subsection{Oscillating Scores}
@@
 
-In an attempt to find a training session mathcing this quality
-
-% grid search results.
 \subsection{Model Evolution}
@@
 \subsection{Interpreting Communcation Vectors}
-Unfortunately, we could not 
+Unfortunately, we could not fully interpret the communication vectors due to the
+disconnect between representation of information. However, we found an 
+interesting result when the players were given no identifying information (e.g. 
+there were no sabotages whatsoever in the percpetion stage), the crew could still
+win the situation. At first glance, this seems almost impossible because the crew would
+be unable to identify the imposters via the necessary events. Further thought lead us
+to make an estimated conclusion that the crew model was actual creating a hidden tag or key
+to identify themselves within the commmunication stage, therefore identifying the imposters 
+immediately. The imposters would then have to train to figure out this key or
+become helpless. This situation resembles almost a cryptographic adversarial problem,
+unlocking more future directions this work could potentially travel.
 \subsection{Future Directions}
@@
 \section{Reproducibility}
+Reproducibility might yield different results due to the random creation of data and
+weight setting.
+
+The parameters used for Figure 2, the grid search, are:
+
+\begin{tabular}{ |c|c| } 
+\hline 
+"B" & 64 \\
+\hline
+"N" & 16 \\
+\hline
+"H"& 256 \\
+\hline
+"M"& 12 \\
+\hline
+"ROUNDS"& 0 \\
+\hline
+"P"& 10 \\
+\hline
+"I"& 2 \\
+\hline
+"EPOCHS"& 6 \\
+\hline
+"EPOCH LENGTH"& 1024 \\
+\hline
+"VIEW CHANCE"& 0.5 \\
+\hline
+"SABOTAGE CHANCE"& 0.5 \\
+\hline
+"TRAIN CREW FIRST"& false \\
+\hline
+"TRAIN SINGLE CREWMATE"& true \\
+\hline
+"CONST CREW COPY FREQ"& 32 \\
+\hline
+"TRAIN SINGLE IMPOSTER"& true \\
+\hline
+"CONST IMPOSTER COPY FREQ"& 32 \\
+\hline
+"PRINT FREQ"& 64 \\
+\hline
+"SAVE EPOCH FREQ"& 2 \\
+\hline
+\end{tabular}
 \section{Framework}
+The framework we used for our project
+was PyTorch, and build the model based off of their implementation
+of an LSTM and MLP layers. 
 \end{document}

### 2020-12-03 paper/main.tex
almost there. mainly just abstract left

@@
 to pass information between each other in multiple rounds.
+Figure \ref{fig:model} shows a simplified diagram of the complete
+architecture.
 
@@
       \caption{A grid search heat map over the size parameters M (message vector) 
-      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs.
+      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs. Figure \ref{tab:params} contains the other parameters used.
       }
-   \label{fig:model}
+   \label{fig:grid}
 \end{figure*}
 \section{Results}
-% talk about our goal for a qualitatively "good" communication
-% session.
 Due to the unprecedented architecture, we decided our overall goals
@@
 which were considered as the "initialization" of the two models. Training the imposters
-first gave them time to learn to note vote for each other. Then, the crew
+first gave them time to learn to not vote for each other. Then, the crew
 had learned the same thing on the next epoch. After this initial training,
@@
 are successfunlly balanced and able to improve their strategy with training time against
-the opposition.
+the opposition. Figure \ref{fig:osc} shows an example of a single run which converges
+to a crew score of around 0.6.
+\begin{figure}[h]
+   \begin{center}
+      \includegraphics[width=0.47827\textwidth]{img/m16_r10.png}
+   \end{center}
 
-\subsection{Model Evolution}
-% are the agents "improving" or just changing minorly to trick each other
+   \label{fig:osc}
+   \caption{Crew score over time for a particular training run. The crew model is
+   being trained in odd epochs, and imposters in even epochs.}
+\end{figure}
+
 \subsection{Interpreting Communcation Vectors}
-Unfortunately, we could not fully interpret the communication vectors due to the
+Unfortunately, we were not able to interpret the communication vectors due to the
 disconnect between representation of information. However, we found an 
@@
 \section{Reproducibility}
-Reproducibility might yield different results due to the random creation of data and
-weight setting.
+The code that we used to train, test, and plot graphics for the models
+is in a public GitHub repository at \url{https://github.com/quinquice/mendax}.
+Note that due to random data generation and unpredictable training, it may be
+difficult to reproduce the exact graphs we have in this paper, but similar results
+should be attainable.
 
-The parameters used for Figure 2, the grid search, are:
-
+\begin{figure}
+   \centering
 \begin{tabular}{ |c|c| } 
@@
 "H"& 256 \\
-\hline
-"M"& 12 \\
-\hline
-"ROUNDS"& 0 \\
 \hline
@@
 \hline
-"PRINT FREQ"& 64 \\
-\hline
-"SAVE EPOCH FREQ"& 2 \\
-\hline
 \end{tabular}
+\caption{The parameters used for Figure \ref{fig:grid}, the grid search}
+\label{tab:params}
+\end{figure}
+
 \section{Framework}
@@
 was PyTorch, and build the model based off of their implementation
-of an LSTM and MLP layers. 
+of an LSTM and MLP layers. Models were trained on a variety of different
+computers, sometimes with CPU and sometimes with GPU.
+
 \end{document}

### 2020-12-03 paper/main.tex
finalize paper, clean up repository

@@
 
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
 \usepackage[breaklinks=true,bookmarks=false]{hyperref}
@@
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
 \setcounter{page}{1}
@@
 %%%%%%%%% TITLE
-\title{Machines are Among Us}
+\title{The Machines are Among Us}
 
@@
 {\tt\small zjminot@gatech.edu}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
 \and
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+   In this paper, we explore techniques for training sets of deep adversarial neural networks
+   to communicate with each other. In order to investigate this, we took inspiration
+   from the game Among Us to develop a scenario in which multiple agents could
+   communicate and compete with each other. By running a variety of tests spanning
+   many conditions for the sets of networks, we learn that communication between
+   these networks is volatile, and that often simply the process of developing a
+   common ``language'' of communication between multiple networks poses
+   challenges.
 \end{abstract}
